---
title: "Example code for calculating PDD and FUV of LAPS sensitivity runs"
author: Johanna LK Wren and Taylor Ely
date: June 29, 2021
output:
  html_notebook:
    theme: flatly
    toc: true
    toc_float:
      collapsed: false
      tod_depth: 3
---

# Description
### This code takes a trajectory file generated by OceanParcels, calculates particle density distributions (PDD), and calculated FUVs between 2 PDDs

```{r}
#load libraries
library(ncdf4)
library(dplyr)
library(MASS)
```

# Read in trajectory file
### The OceanParcls output file consists of lat, lon, and age (and others) for each particle. One column is one particle, the number of rows is number of time steps. 

```{r}
# Create function to read in trajectory file at a particular day
load_netcdf<-function(datafile, subsetday){
  dat <- nc_open(datafile)
  lo <- ncvar_get(dat, 'lon')
  la <- ncvar_get(dat, 'lat')
  a <- ncvar_get(dat, 'age')
  site<-ncvar_get(dat, 'releaseSite')
  nc_close(dat)
  idx <- which(a == subsetday*86400)
  output <<- bind_cols(lon=lo[idx], lat=la[idx], site=site[idx]) 
}

m0_30<-load_netcdf('/Users/taylorely/Documents/OceanModeling/LAPS_sensitivity_n1_pld180_0m_Kh0_nday545_daily_2013_2.nc',30)
m0_60<-load_netcdf('/Users/taylorely/Documents/OceanModeling/LAPS_sensitivity_n1_pld180_0m_Kh0_nday545_daily_2013_2.nc',60)
m0_90<-load_netcdf('/Users/taylorely/Documents/OceanModeling/LAPS_sensitivity_n1_pld180_0m_Kh0_nday545_daily_2013_2.nc',90)
m0_180<-load_netcdf('/Users/taylorely/Documents/OceanModeling/LAPS_sensitivity_n1_pld180_0m_Kh0_nday545_daily_2013_2.nc',180)

m5_30<-load_netcdf('/Users/taylorely/Documents/OceanModeling/LAPS_sensitivity_n1_pld180_5m_Kh0_nday545_daily_2013_2.nc',30)
m5_60<-load_netcdf('/Users/taylorely/Documents/OceanModeling/LAPS_sensitivity_n1_pld180_5m_Kh0_nday545_daily_2013_2.nc',60)
m5_90<-load_netcdf('/Users/taylorely/Documents/OceanModeling/LAPS_sensitivity_n1_pld180_5m_Kh0_nday545_daily_2013_2.nc',90)
m5_180<-load_netcdf('/Users/taylorely/Documents/OceanModeling/LAPS_sensitivity_n1_pld180_5m_Kh0_nday545_daily_2013_2.nc',180)

m10_30<-load_netcdf('/Users/taylorely/Documents/OceanModeling/LAPS_sensitivity_n1_pld180_10m_Kh0_nday545_daily_2013_2.nc',30)
m10_60<-load_netcdf('/Users/taylorely/Documents/OceanModeling/LAPS_sensitivity_n1_pld180_10m_Kh0_nday545_daily_2013_2.nc',60)
m10_90<-load_netcdf('/Users/taylorely/Documents/OceanModeling/LAPS_sensitivity_n1_pld180_10m_Kh0_nday545_daily_2013_2.nc',90)
m10_180<-load_netcdf('/Users/taylorely/Documents/OceanModeling/LAPS_sensitivity_n1_pld180_10m_Kh0_nday545_daily_2013_2.nc',180)

m20_30<-load_netcdf('/Users/taylorely/Documents/OceanModeling/LAPS_sensitivity_n1_pld180_20m_Kh0_nday545_daily_2013_2.nc',30)
m20_60<-load_netcdf('/Users/taylorely/Documents/OceanModeling/LAPS_sensitivity_n1_pld180_20m_Kh0_nday545_daily_2013_2.nc',60)
m20_90<-load_netcdf('/Users/taylorely/Documents/OceanModeling/LAPS_sensitivity_n1_pld180_20m_Kh0_nday545_daily_2013_2.nc',90)
m20_180<-load_netcdf('/Users/taylorely/Documents/OceanModeling/LAPS_sensitivity_n1_pld180_20m_Kh0_nday545_daily_2013_2.nc',180)

m30_30<-load_netcdf('/Users/taylorely/Documents/OceanModeling/LAPS_sensitivity_n1_pld180_30m_Kh0_nday545_daily_2013_2.nc',30)
m30_60<-load_netcdf('/Users/taylorely/Documents/OceanModeling/LAPS_sensitivity_n1_pld180_30m_Kh0_nday545_daily_2013_2.nc',60)
m30_90<-load_netcdf('/Users/taylorely/Documents/OceanModeling/LAPS_sensitivity_n1_pld180_30m_Kh0_nday545_daily_2013_2.nc',90)
m30_180<-load_netcdf('/Users/taylorely/Documents/OceanModeling/LAPS_sensitivity_n1_pld180_30m_Kh0_nday545_daily_2013_2.nc',180)

m50_30<-load_netcdf('/Users/taylorely/Documents/OceanModeling/LAPS_sensitivity_n1_pld180_50m_Kh0_nday545_daily_2013_2.nc',30)
m50_60<-load_netcdf('/Users/taylorely/Documents/OceanModeling/LAPS_sensitivity_n1_pld180_50m_Kh0_nday545_daily_2013_2.nc',60)
m50_90<-load_netcdf('/Users/taylorely/Documents/OceanModeling/LAPS_sensitivity_n1_pld180_50m_Kh0_nday545_daily_2013_2.nc',90)
m50_180<-load_netcdf('/Users/taylorely/Documents/OceanModeling/LAPS_sensitivity_n1_pld180_50m_Kh0_nday545_daily_2013_2.nc',180)

avg25_30<-load_netcdf('/Users/taylorely/Documents/OceanModeling/LAPS_sensitivity_n1_pld180_25avg_Kh0_nday545_daily_2013_2.nc',30)
avg25_60<-load_netcdf('/Users/taylorely/Documents/OceanModeling/LAPS_sensitivity_n1_pld180_25avg_Kh0_nday545_daily_2013_2.nc',60)
avg25_90<-load_netcdf('/Users/taylorely/Documents/OceanModeling/LAPS_sensitivity_n1_pld180_25avg_Kh0_nday545_daily_2013_2.nc',90)
avg25_180<-load_netcdf('/Users/taylorely/Documents/OceanModeling/LAPS_sensitivity_n1_pld180_25avg_Kh0_nday545_daily_2013_2.nc',180)

avg50_30<-load_netcdf('/Users/taylorely/Documents/OceanModeling/LAPS_sensitivity_n1_pld180_50avg_Kh0_nday545_daily_2013_2.nc',30)
avg50_60<-load_netcdf('/Users/taylorely/Documents/OceanModeling/LAPS_sensitivity_n1_pld180_50avg_Kh0_nday545_daily_2013_2.nc',60)
avg50_90<-load_netcdf('/Users/taylorely/Documents/OceanModeling/LAPS_sensitivity_n1_pld180_50avg_Kh0_nday545_daily_2013_2.nc',90)
avg50_180<-load_netcdf('/Users/taylorely/Documents/OceanModeling/LAPS_sensitivity_n1_pld180_50avg_Kh0_nday545_daily_2013_2.nc',180)

#load n100 with diff days
n100_day30<-load_netcdf('/home/tely/LAPS/n100_day30_new.nc',30)
n100_day60<-load_netcdf('/home/tely/LAPS/n100_day60_new.nc',60)
n100_day90<-load_netcdf('/home/tely/LAPS/n100_day90_new.nc',90)
n100_day180<-load_netcdf('/home/tely/LAPS/n100_day180_new.nc',180)

#load n100 2nd run with diff days
#n100_repeat_day30<-load_netcdf('n100_repeat_day30.nc',30)
#n100_repeat_day60<-load_netcdf('n100_repeat_day60.nc',60)
#n100_repeat_day90<-load_netcdf('n100_repeat_day90.nc',90)
#n100_repeat_day180<-load_netcdf('n100_repeat_day180.nc',180)

#load n250 with diff days
n250_day30<-load_netcdf('/home/tely/LAPS/n250_day30_new.nc',30)
n250_day60<-load_netcdf('/home/tely/LAPS/n250_day60_new.nc',60)
n250_day90<-load_netcdf('/home/tely/LAPS/n250_day90_new.nc',90)
n250_day180<-load_netcdf('/home/tely/LAPS/n250_day180_new.nc',180)

#n250 repeat
n250_day30_repeat<-load_netcdf('/home/tely/LAPS/n250_day180_new_repeat.nc',30)
n250_day60_repeat<-load_netcdf('/home/tely/LAPS/n250_day180_new_repeat.nc',60)
n250_day90_repeat<-load_netcdf('/home/tely/LAPS/n250_day180_new_repeat.nc',90)
n250_day180_repeat<-load_netcdf('/home/tely/LAPS/n250_day180_new_repeat.nc',180)

#load n500 with diff days
n500_day30<-load_netcdf('/home/tely/LAPS/n500_day30_new.nc',30)
n500_day60<-load_netcdf('/home/tely/LAPS/n500_day60_new.nc',60)
n500_day90<-load_netcdf('/home/tely/LAPS/n500_day90_new.nc',90)
n500_day180<-load_netcdf('/home/tely/LAPS/n500_day180_new.nc',180)

#load n750 with diff days, the reason this set is divided into thirds is because the model crashes when running the entire thing so this number of particles was run with the release sites divided up into thirds and then merged after for stats and comparisons
#n750_1_day90<-load_netcdf('n750_day90_first.nc',30)
#n750_1_day60<-load_netcdf('n750_day60_first.nc',60)
#n750_1_day90<-load_netcdf('n750_day90_first.nc',90)
#n750_1_day180<-load_netcdf('n750_day180_first.nc',180)
#
#n750_2_day90<-load_netcdf('n750_day90_second.nc',30)
#n750_2_day60<-load_netcdf('n750_day60_second.nc',60)
#n750_2_day90<-load_netcdf('n750_day90_second.nc',90)
#n750_2_day180<-load_netcdf('n750_day180_second.nc',180)
#
#n750_3_day90<-load_netcdf('n750_day90_third.nc',30)
#n750_3_day60<-load_netcdf('n750_day60_third.nc',60)
#n750_3_day90<-load_netcdf('n750_day90_third.nc',90)
#n750_3_day180<-load_netcdf('n750_day180_third.nc',180)
#
## bind these together
#n750_day90<-rbind(n750_1_day90,n750_2_day90,n750_3_day90)
#rm(n750_1_day90) # running this code is memory intensive so it is good to #remove unnecessary things
#rm(n750_2_day90)
#rm(n750_3_day90)
#
#n750_day60<-rbind(n750_1_day60,n750_2_day60,n750_3_day60)
#rm(n750_1_day60)
#rm(n750_2_day60)
#rm(n750_3_day60)
#
#n750_day90<-rbind(n750_1_day90,n750_2_day90,n750_3_day90)
#rm(n750_1_day90)
#rm(n750_2_day90)
#rm(n750_3_day90)
#
#n750_day180<-rbind(n750_1_day180,n750_2_day180,n750_3_day180)
#rm(n750_1_day180)
#rm(n750_2_day180)
#rm(n750_3_day180)


#load n1000 with diff days, the reason this set is divided into thirds is because the model crashes when running the entire thing so this number of particles was run with the release sites divided up into thirds and then merged after for stats and comparisons
n1000_1_day30<-load_netcdf('/home/tely/LAPS/n1000_day30_new_site1.nc',30)
n1000_1_day60<-load_netcdf('/home/tely/LAPS/n1000_day60_new_site1.nc',60)
n1000_1_day90<-load_netcdf('/home/tely/LAPS/n1000_day90_new_site1.nc',90)
n1000_1_day180<-load_netcdf('/home/tely/LAPS/n1000_day180_new_site1.nc',180)

n1000_2_day30<-load_netcdf('/home/tely/LAPS/n1000_day30_new_site2.nc',30)
n1000_2_day60<-load_netcdf('/home/tely/LAPS/n1000_day60_new_site2.nc',60)
n1000_2_day90<-load_netcdf('/home/tely/LAPS/n1000_day90_new_site2.nc',90)
n1000_2_day180<-load_netcdf('/home/tely/LAPS/n1000_day180_new_site2.nc',180)

n1000_6_day30<-load_netcdf('/home/tely/LAPS/n1000_day30_new_site6.nc',30)
n1000_6_day60<-load_netcdf('/home/tely/LAPS/n1000_day60_new_site6.nc',60)
n1000_6_day90<-load_netcdf('/home/tely/LAPS/n1000_day90_new_site6.nc',90)
n1000_6_day180<-load_netcdf('/home/tely/LAPS/n1000_day180_new_site6.nc',180)

n1000_7_1_day30<-load_netcdf('/home/tely/LAPS/n1000_day30_new_site7_1.nc',30)
n1000_7_1_day60<-load_netcdf('/home/tely/LAPS/n1000_day60_new_site7_1.nc',60)
n1000_7_1_day90<-load_netcdf('/home/tely/LAPS/n1000_day90_new_site7_1.nc',90)
n1000_7_1_day180<-load_netcdf('/home/tely/LAPS/n1000_day180_new_site7_1.nc',180)

n1000_7_2_day30<-load_netcdf('/home/tely/LAPS/n1000_day30_new_site7_2.nc',30)
n1000_7_2_day60<-load_netcdf('/home/tely/LAPS/n1000_day60_new_site7_2.nc',60)
n1000_7_2_day90<-load_netcdf('/home/tely/LAPS/n1000_day90_new_site7_2.nc',90)
n1000_7_2_day180<-load_netcdf('/home/tely/LAPS/n1000_day180_new_site7_2.nc',180)

n1000_12_day30<-load_netcdf('/home/tely/LAPS/n1000_day30_new_site12.nc',30)
n1000_12_day60<-load_netcdf('/home/tely/LAPS/n1000_day60_new_site12.nc',60)
n1000_12_day90<-load_netcdf('/home/tely/LAPS/n1000_day90_new_site12.nc',90)
n1000_12_day180<-load_netcdf('/home/tely/LAPS/n1000_day180_new_site12.nc',180)

n1000_other_day30<-load_netcdf('/home/tely/LAPS/n1000_day30_new_siteother.nc',30)
n1000_other_day60<-load_netcdf('/home/tely/LAPS/n1000_day60_new_siteother.nc',60)
n1000_other_day90<-load_netcdf('/home/tely/LAPS/n1000_day90_new_siteother.nc',90)
n1000_other_day180<-load_netcdf('/home/tely/LAPS/n1000_day180_new_siteother.nc',180)

# bind these together
n1000_day30<-rbind(n1000_1_day30,n1000_2_day30,n1000_6_day30,n1000_7_1_day30,n1000_7_2_day30,n1000_12_day30,n1000_other_day30)
rm(n1000_1_day30) # running this code is memory intensive so it is good to remove unnecessary things
rm(n1000_2_day30)
rm(n1000_3_day30)

n1000_day60<-rbind(n1000_1_day60,n1000_2_day60,n1000_6_day60,n1000_7_1_day60,n1000_7_2_day60,n1000_12_day60,n1000_other_day60)
rm(n1000_1_day60)
rm(n1000_2_day60)
rm(n1000_3_day60)

n1000_day90<-rbind(n1000_1_day90,n1000_2_day90,n1000_6_day90,n1000_7_1_day90,n1000_7_2_day90,n1000_12_day90,n1000_other_day90)

rm(n1000_1_day90)
rm(n1000_2_day90)
rm(n1000_3_day90)

n1000_day180<-rbind(n1000_1_day180,n1000_2_day180,n1000_6_day180,n1000_7_1_day180,n1000_7_2_day180,n1000_12_day180,n1000_other_day180)

rm(n1000_1_day180)
rm(n1000_2_day180)
rm(n1000_3_day180)

```


# Calculate the PDDs using the MASS package
```{r}
# Create a function to calculate PDDs
densitydist<-function(input,xboxes,yboxes){
  dd <- kde2d(input$lon, input$lat, n=c(xboxes,yboxes),lims=c(120,240,0,50)) 
  str(dd)
  dd_df <<-data.frame(expand.grid(dd$x, dd$y), density=as.vector(dd$z))
}


dd30_0m<-densitydist(m0_30,350,150)
names(dd30_0m)[1:2] <- c('lon', 'lat') 

dd60_0m<-densitydist(m0_60,350,150)
names(dd60_0m)[1:2] <- c('lon', 'lat') 

dd90_0m<-densitydist(m0_90,350,150)
names(dd90_0m)[1:2] <- c('lon', 'lat') 

dd180_0m<-densitydist(m0_180,350,150)
names(dd180_0m)[1:2] <- c('lon', 'lat') 


dd30_5m<-densitydist(m5_30,350,150)
names(dd30_5m)[1:2] <- c('lon', 'lat') 

dd60_5m<-densitydist(m5_60,350,150)
names(dd60_5m)[1:2] <- c('lon', 'lat') 

dd90_5m<-densitydist(m5_90,350,150)
names(dd90_5m)[1:2] <- c('lon', 'lat') 

dd180_5m<-densitydist(m5_180,350,150)
names(dd180_5m)[1:2] <- c('lon', 'lat') 


dd30_10m<-densitydist(m10_30,350,150)
names(dd30_10m)[1:2] <- c('lon', 'lat') 

dd60_10m<-densitydist(m10_60,350,150)
names(dd60_10m)[1:2] <- c('lon', 'lat') 

dd90_10m<-densitydist(m10_90,350,150)
names(dd90_10m)[1:2] <- c('lon', 'lat') 

dd180_10m<-densitydist(m10_180,350,150)
names(dd180_10m)[1:2] <- c('lon', 'lat') 


dd30_20m<-densitydist(m20_30,350,150)
names(dd30_20m)[1:2] <- c('lon', 'lat') 
 
dd60_20m<-densitydist(m20_60,350,150)
names(dd60_20m)[1:2] <- c('lon', 'lat') 

dd90_20m<-densitydist(m20_90,350,150)
names(dd90_20m)[1:2] <- c('lon', 'lat') 

dd180_20m<-densitydist(m20_180,350,150)
names(dd180_20m)[1:2] <- c('lon', 'lat') 


dd30_30m<-densitydist(m30_30,350,150)
names(dd30_30m)[1:2] <- c('lon', 'lat') 

dd60_30m<-densitydist(m30_60,350,150)
names(dd60_30m)[1:2] <- c('lon', 'lat') 

dd90_30m<-densitydist(m30_90,350,150)
names(dd90_30m)[1:2] <- c('lon', 'lat') 

dd180_30m<-densitydist(m30_180,350,150)
names(dd180_30m)[1:2] <- c('lon', 'lat') 


dd30_50m<-densitydist(m50_30,350,150)
names(dd30_50m)[1:2] <- c('lon', 'lat') 
 
dd60_50m<-densitydist(m50_60,350,150)
names(dd60_50m)[1:2] <- c('lon', 'lat') 

dd90_50m<-densitydist(m50_90,350,150)
names(dd90_50m)[1:2] <- c('lon', 'lat') 

dd180_50m<-densitydist(m50_180,350,150)
names(dd180_50m)[1:2] <- c('lon', 'lat') 

dd30_50avg<-densitydist(avg50_30,350,150)
names(dd30_50avg)[1:2] <- c('lon', 'lat') 
dd60_50avg<-densitydist(avg50_60,350,150)
names(dd60_50avg)[1:2] <- c('lon', 'lat') 
dd90_50avg<-densitydist(avg50_90,350,150)
names(dd90_50avg)[1:2] <- c('lon', 'lat') 
dd180_50avg<-densitydist(avg50_180,350,150)
names(dd180_50avg)[1:2] <- c('lon', 'lat') 

dd30_25avg<-densitydist(avg25_30,350,150)
names(dd30_25avg)[1:2] <- c('lon', 'lat') 
dd60_25avg<-densitydist(avg25_60,350,150)
names(dd60_25avg)[1:2] <- c('lon', 'lat') 
dd90_25avg<-densitydist(avg25_90,350,150)
names(dd90_25avg)[1:2] <- c('lon', 'lat') 
dd180_25avg<-densitydist(avg25_180,350,150)
names(dd180_25avg)[1:2] <- c('lon', 'lat') 

#100 particles
dd30_n100<-densitydist(n100_day30,350,150)
names(dd30_n100)[1:2] <- c('lon', 'lat') # this just renames the file
rm(n100_day30) # remove unneccesary things
write.csv(dd30_n100,file="/home/tely/LAPS/dd30_n100_new.csv")# write this to a file because sometimes this R file runs out of memory so to account fo this you can wipe the memory after running each of these files and the load back in the PDD files later for calculating the FUV. For other sensitivity tests this wasn't necessary but for this one it was. 
rm(dd30_n100)

dd60_n100<-densitydist(n100_day60,350,150)
names(dd60_n100)[1:2] <- c('lon', 'lat')
rm(n100_day60)
write.csv(dd60_n100,file="/home/tely/LAPS/dd60_n100_new.csv")
rm(dd60_n100)

dd90_n100<-densitydist(n100_day90,350,150)
names(dd90_n100)[1:2] <- c('lon', 'lat')
rm(n100_day90)
write.csv(dd90_n100,file="/home/tely/LAPS/dd90_n100_new.csv")
rm(dd90_n100)

dd180_n100<-densitydist(n100_day180,350,150)
names(dd180_n100)[1:2] <- c('lon', 'lat')
rm(n100_day180)
write.csv(dd180_n100,file="/home/tely/LAPS/dd180_n100_new.csv")
rm(dd180_n100)

#100 particles repeat
#dd30_n100_repeat<-densitydist(n100_repeat_day30,350,150)
#names(dd30_n100_repeat)[1:2] <- c('lon', 'lat')
#rm(n100_repeat_day30)
#write.csv(dd30_n100_repeat,file="/home/tely/LAPS/dd30_n100_repeat.csv")
#rm(dd30_n100_repeat)
#
#dd60_n100_repeat<-densitydist(n100_repeat_day60,350,150)
#names(dd60_n100_repeat)[1:2] <- c('lon', 'lat')
#rm(n100_repeat_day60)
#write.csv(dd60_n100_repeat,file="/home/tely/LAPS/dd60_n100_repeat.csv")
#rm(dd60_n100_repeat)
#
#dd90_n100_repeat<-densitydist(n100_repeat_day90,350,150)
#names(dd90_n100_repeat)[1:2] <- c('lon', 'lat')
#rm(n100_repeat_day90)
#write.csv(dd90_n100_repeat,file="/home/tely/LAPS/dd90_n100_repeat.csv")
#rm(dd90_n100_repeat)
#
#dd180_n100_repeat<-densitydist(n100_repeat_day180,350,150)
#names(dd180_n100_repeat)[1:2] <- c('lon', 'lat')
#rm(n100_repeat_day180)
#write.csv(dd180_n100_repeat,file="/home/tely/LAPS/dd180_n100_repeat.csv")
#rm(dd180_n100_repeat)

#250 particles
dd30_n250<-densitydist(n250_day30,350,150)
names(dd30_n250)[1:2] <- c('lon', 'lat')
rm(n250_day30)
write.csv(dd30_n250,file="/home/tely/LAPS/dd30_n250_new.csv")
rm(dd30_n250)

dd60_n250<-densitydist(n250_day60,350,150)
names(dd60_n250)[1:2] <- c('lon', 'lat')
rm(n250_day60)
write.csv(dd60_n250,file="/home/tely/LAPS/dd60_n250_new.csv")
rm(dd60_n250)

dd90_n250<-densitydist(n250_day90,350,150)
names(dd90_n250)[1:2] <- c('lon', 'lat')
rm(n250_day90)
write.csv(dd90_n250,file="/home/tely/LAPS/dd90_n250_new.csv")
rm(dd90_n250)

dd180_n250<-densitydist(n250_day180,350,150)
names(dd180_n250)[1:2] <- c('lon', 'lat')
rm(n250_day180)
write.csv(dd180_n250,file="/home/tely/LAPS/dd180_n250_new.csv")
rm(dd180_n250)

#250 particles repeat
dd30_n250_repeat<-densitydist(n250_day30_repeat,350,150)
names(dd30_n250_repeat)[1:2] <- c('lon', 'lat')
rm(n250_day30_repeat)
write.csv(dd30_n250_repeat,file="/home/tely/LAPS/dd30_n250_new_repeat.csv")
rm(dd30_n250_repeat)

dd60_n250_repeat<-densitydist(n250_day60_repeat,350,150)
names(dd60_n250_repeat)[1:2] <- c('lon', 'lat')
rm(n250_day60_repeat)
write.csv(dd60_n250_repeat,file="/home/tely/LAPS/dd60_n250_new_repeat.csv")
rm(dd60_n250_repeat)

dd90_n250_repeat<-densitydist(n250_day90_repeat,350,150)
names(dd90_n250_repeat)[1:2] <- c('lon', 'lat')
rm(n250_day90_repeat)
write.csv(dd90_n250_repeat,file="/home/tely/LAPS/dd90_n250_new_repeat.csv")
rm(dd90_n250_repeat)

dd180_n250_repeat<-densitydist(n250_day180_repeat,350,150)
names(dd180_n250_repeat)[1:2] <- c('lon', 'lat')
rm(n250_day180_repeat)
write.csv(dd180_n250_repeat,file="/home/tely/LAPS/dd180_n250_new_repeat.csv")
rm(dd180_n250_repeat)

#500 particles
dd30_n500<-densitydist(n500_day30,350,150)
names(dd30_n500)[1:2] <- c('lon', 'lat')
rm(n500_day30)
write.csv(dd30_n500,file="/home/tely/LAPS/dd30_n500_new.csv")
rm(dd30_n500)

dd60_n500<-densitydist(n500_day60,350,150)
names(dd60_n500)[1:2] <- c('lon', 'lat')
rm(n500_day60)
write.csv(dd60_n500,file="/home/tely/LAPS/dd60_n500_new.csv")
rm(dd60_n500)

dd90_n500<-densitydist(n500_day90,350,150)
names(dd90_n500)[1:2] <- c('lon', 'lat')
rm(n500_day90)
write.csv(dd90_n500,file="/home/tely/LAPS/dd90_n500_new.csv")
rm(dd90_n500)

dd180_n500<-densitydist(n500_day180,350,150)
names(dd180_n500)[1:2] <- c('lon', 'lat')
rm(n500_day180)
write.csv(dd180_n500,file="/home/tely/LAPS/dd180_n500_new.csv")
rm(dd180_n500)

#750 particles
#dd <- kde2d(n750_day30$lon, n750_day30$lat, n=c(350,150),lims=c(120,240,0,50))
#dd30_n750<-densitydist(n750_day30,350,150)
#names(dd30_n750)[1:2] <- c('lon', 'lat')
#rm(n750_day30)
#write.csv(dd30_n750,file="/home/tely/LAPS/dd30_n750.csv")
#rm(dd30_n750)
#
#rm(output)
#dd60_n750<-densitydist(n750_day60,350,150)
#names(dd60_n750)[1:2] <- c('lon', 'lat')
#rm(n750_day60)
#write.csv(dd60_n750,file="/home/tely/LAPS/dd60_n750.csv")
#rm(dd60_n750)
#
#dd90_n750<-densitydist(n750_day90,350,150)
#names(dd90_n750)[1:2] <- c('lon', 'lat')
#rm(n750_day90)
#write.csv(dd90_n750,file="/home/tely/LAPS/dd90_n750.csv")
#rm(dd90_n750)
#
#dd180_n750<-densitydist(n750_day180,350,150)
#names(dd180_n750)[1:2] <- c('lon', 'lat')
#rm(n750_day180)
#write.csv(dd180_n750,file="/home/tely/LAPS/dd180_n750.csv")
#rm(dd180_n750)

#1000 particles
dd30_n1000<-densitydist(n1000_day30,350,150)
names(dd30_n1000)[1:2] <- c('lon', 'lat')
rm(n1000_day30)
write.csv(dd30_n1000,file="/home/tely/LAPS/dd30_n1000.csv")
rm(dd30_n1000)

dd60_n1000<-densitydist(n1000_day60,350,150)
names(dd60_n1000)[1:2] <- c('lon', 'lat')
rm(n1000_day60)
write.csv(dd60_n1000,file="/home/tely/LAPS/dd60_n1000.csv")
rm(dd60_n1000)

dd90_n1000<-densitydist(n1000_day90,350,150)
names(dd90_n1000)[1:2] <- c('lon', 'lat')
rm(n1000_day90)
write.csv(dd90_n1000,file="/home/tely/LAPS/dd90_n1000.csv")
rm(dd90_n1000)

dd180_n1000<-densitydist(n1000_day180,350,150)
names(dd180_n1000)[1:2] <- c('lon', 'lat')
rm(n1000_day180)
write.csv(dd180_n1000,file="/home/tely/LAPS/dd180_n1000.csv")
rm(dd180_n1000)

```

# Calculate the FUV by 1-R^2
```{r}
# Load the files back in (because the previous steps needed the full amount of memory)
#between 100 and 100 repeat
dd30_n100<-read.csv("/home/tely/LAPS/dd30_n100_new.csv", stringsAsFactors = F,header = TRUE)
dd30_n100<-dd30_n100[2:4]
dd60_n100<-read.csv("/home/tely/LAPS/dd60_n100_new.csv",stringsAsFactors = F,header = TRUE)
dd60_n100<-dd60_n100[2:4]
dd90_n100<-read.csv("/home/tely/LAPS/dd90_n100_new.csv", stringsAsFactors = F,header = TRUE)
dd90_n100<-dd90_n100[2:4]
dd180_n100<-read.csv("/home/tely/LAPS/dd180_n100_new.csv",stringsAsFactors = F,header = TRUE)
dd180_n100<-dd180_n100[2:4]

#dd30_n100_repeat<-read.csv("dd30_n100_repeat.csv", stringsAsFactors = #F,header = TRUE)
#dd30_n100_repeat<-dd30_n100_repeat[2:4]
#dd60_n100_repeat<-read.csv("dd60_n100_repeat.csv",stringsAsFactors = #F,header = TRUE)
#dd60_n100_repeat<-dd60_n100_repeat[2:4]
#dd90_n100_repeat<-read.csv("dd90_n100_repeat.csv", stringsAsFactors = #F,header = TRUE)
#dd90_n100_repeat<-dd90_n100_repeat[2:4]
#dd180_n100_repeat<-read.csv("dd180_n100_repeat.csv",stringsAsFactors = #F,header = TRUE)
#dd180_n100_repeat<-dd180_n100_repeat[2:4]

dd30_n250<-read.csv("/home/tely/LAPS/dd30_n250_new.csv", stringsAsFactors = F,header = TRUE)
dd30_n250<-dd30_n250[2:4]
dd60_n250<-read.csv("/home/tely/LAPS/dd60_n250_new.csv",stringsAsFactors = F,header = TRUE)
dd60_n250<-dd60_n250[2:4]
dd90_n250<-read.csv("/home/tely/LAPS/dd90_n250_new.csv", stringsAsFactors = F,header = TRUE)
dd90_n250<-dd90_n250[2:4]
dd180_n250<-read.csv("/home/tely/LAPS/dd180_n250_new.csv",stringsAsFactors = F,header = TRUE)
dd180_n250<-dd180_n250[2:4]

dd30_n250_repeat<-read.csv("/home/tely/LAPS/dd30_n250_new_repeat.csv", stringsAsFactors = F,header = TRUE)
dd30_n250_repeat<-dd30_n250_repeat[2:4]
dd60_n250_repeat<-read.csv("/home/tely/LAPS/dd60_n250_new_repeat.csv",stringsAsFactors = F,header = TRUE)
dd60_n250_repeat<-dd60_n250_repeat[2:4]
dd90_n250_repeat<-read.csv("/home/tely/LAPS/dd90_n250_new_repeat.csv", stringsAsFactors = F,header = TRUE)
dd90_n250_repeat<-dd90_n250_repeat[2:4]
dd180_n250_repeat<-read.csv("/home/tely/LAPS/dd180_n250_new_repeat.csv",stringsAsFactors = F,header = TRUE)
dd180_n250_repeat<-dd180_n250_repeat[2:4]

dd30_n500<-read.csv("/home/tely/LAPS/dd30_n500_new.csv", stringsAsFactors = F,header = TRUE)
dd30_n500<-dd30_n500[2:4]
dd60_n500<-read.csv("/home/tely/LAPS/dd60_n500_new.csv",stringsAsFactors = F,header = TRUE)
dd60_n500<-dd60_n500[2:4]
dd90_n500<-read.csv("/home/tely/LAPS/dd90_n500_new.csv", stringsAsFactors = F,header = TRUE)
dd90_n500<-dd90_n500[2:4]
dd180_n500<-read.csv("/home/tely/LAPS/dd180_n500_new.csv",stringsAsFactors = F,header = TRUE)
dd180_n500<-dd180_n500[2:4]

#dd30_n750<-read.csv("dd30_n750.csv", stringsAsFactors = F,header = TRUE)
#dd30_n750<-dd30_n750[2:4]
#dd60_n750<-read.csv("dd60_n750.csv",stringsAsFactors = F,header = TRUE)
#dd60_n750<-dd60_n750[2:4]
#dd90_n750<-read.csv("dd90_n750.csv", stringsAsFactors = F,header = TRUE)
#dd90_n750<-dd90_n750[2:4]
#dd180_n750<-read.csv("dd180_n750.csv",stringsAsFactors = F,header = TRUE)
#dd180_n750<-dd180_n750[2:4]

dd30_n1000<-read.csv("/home/tely/LAPS/dd30_n1000.csv", stringsAsFactors = F,header = TRUE)
dd30_n1000<-dd30_n1000[2:4]
dd60_n1000<-read.csv("/home/tely/LAPS/dd60_n1000.csv",stringsAsFactors = F,header = TRUE)
dd60_n1000<-dd60_n1000[2:4]
dd90_n1000<-read.csv("/home/tely/LAPS/dd90_n1000.csv", stringsAsFactors = F,header = TRUE)
dd90_n1000<-dd90_n1000[2:4]
dd180_n1000<-read.csv("/home/tely/LAPS/dd180_n1000.csv",stringsAsFactors = F,header = TRUE)
dd180_n1000<-dd180_n1000[2:4]
##########################################################################

# Calculate FUV by 1-R^2

fuv_050avg_d30<-1-(cor(dd30_0m$density, dd30_50avg$density, method='pearson')^2)
fuv_050avg_d60<-1-(cor(dd60_0m$density, dd60_50avg$density, method='pearson')^2)
fuv_050avg_d90<-1-(cor(dd90_0m$density, dd90_50avg$density, method='pearson')^2)
fuv_050avg_d180<-1-(cor(dd180_0m$density, dd180_50avg$density, method='pearson')^2)

fuv_550avg_d30<-1-(cor(dd30_5m$density, dd30_50avg$density, method='pearson')^2)
fuv_550avg_d60<-1-(cor(dd60_5m$density, dd60_50avg$density, method='pearson')^2)
fuv_550avg_d90<-1-(cor(dd90_5m$density, dd90_50avg$density, method='pearson')^2)
fuv_550avg_d180<-1-(cor(dd180_5m$density, dd180_50avg$density, method='pearson')^2)

fuv_1050avg_d30<-1-(cor(dd30_10m$density, dd30_50avg$density, method='pearson')^2)
fuv_1050avg_d60<-1-(cor(dd60_10m$density, dd60_50avg$density, method='pearson')^2)
fuv_1050avg_d90<-1-(cor(dd90_10m$density, dd90_50avg$density, method='pearson')^2)
fuv_1050avg_d180<-1-(cor(dd180_10m$density, dd180_50avg$density, method='pearson')^2)

fuv_2050avg_d30<-1-(cor(dd30_20m$density, dd30_50avg$density, method='pearson')^2)
fuv_2050avg_d60<-1-(cor(dd60_20m$density, dd60_50avg$density, method='pearson')^2)
fuv_2050avg_d90<-1-(cor(dd90_20m$density, dd90_50avg$density, method='pearson')^2)
fuv_2050avg_d180<-1-(cor(dd180_20m$density, dd180_50avg$density, method='pearson')^2)

fuv_3050avg_d30<-1-(cor(dd30_30m$density, dd30_50avg$density, method='pearson')^2)
fuv_3050avg_d60<-1-(cor(dd60_30m$density, dd60_50avg$density, method='pearson')^2)
fuv_3050avg_d90<-1-(cor(dd90_30m$density, dd90_50avg$density, method='pearson')^2)
fuv_3050avg_d180<-1-(cor(dd180_30m$density, dd180_50avg$density, method='pearson')^2)

fuv_5050avg_d30<-1-(cor(dd30_50m$density, dd30_50avg$density, method='pearson')^2)
fuv_5050avg_d60<-1-(cor(dd60_50m$density, dd60_50avg$density, method='pearson')^2)
fuv_5050avg_d90<-1-(cor(dd90_50m$density, dd90_50avg$density, method='pearson')^2)
fuv_5050avg_d180<-1-(cor(dd180_50m$density, dd180_50avg$density, method='pearson')^2)
###
fuv_025avg_d30<-1-(cor(dd30_0m$density, dd30_25avg$density, method='pearson')^2)
fuv_025avg_d60<-1-(cor(dd60_0m$density, dd60_25avg$density, method='pearson')^2)
fuv_025avg_d90<-1-(cor(dd90_0m$density, dd90_25avg$density, method='pearson')^2)
fuv_025avg_d180<-1-(cor(dd180_0m$density, dd180_25avg$density, method='pearson')^2)

fuv_525avg_d30<-1-(cor(dd30_5m$density, dd30_25avg$density, method='pearson')^2)
fuv_525avg_d60<-1-(cor(dd60_5m$density, dd60_25avg$density, method='pearson')^2)
fuv_525avg_d90<-1-(cor(dd90_5m$density, dd90_25avg$density, method='pearson')^2)
fuv_525avg_d180<-1-(cor(dd180_5m$density, dd180_25avg$density, method='pearson')^2)

fuv_1025avg_d30<-1-(cor(dd30_10m$density, dd30_25avg$density, method='pearson')^2)
fuv_1025avg_d60<-1-(cor(dd60_10m$density, dd60_25avg$density, method='pearson')^2)
fuv_1025avg_d90<-1-(cor(dd90_10m$density, dd90_25avg$density, method='pearson')^2)
fuv_1025avg_d180<-1-(cor(dd180_10m$density, dd180_25avg$density, method='pearson')^2)

fuv_2025avg_d30<-1-(cor(dd30_20m$density, dd30_25avg$density, method='pearson')^2)
fuv_2025avg_d60<-1-(cor(dd60_20m$density, dd60_25avg$density, method='pearson')^2)
fuv_2025avg_d90<-1-(cor(dd90_20m$density, dd90_25avg$density, method='pearson')^2)
fuv_2025avg_d180<-1-(cor(dd180_20m$density, dd180_25avg$density, method='pearson')^2)

fuv_3025avg_d30<-1-(cor(dd30_30m$density, dd30_25avg$density, method='pearson')^2)
fuv_3025avg_d60<-1-(cor(dd60_30m$density, dd60_25avg$density, method='pearson')^2)
fuv_3025avg_d90<-1-(cor(dd90_30m$density, dd90_25avg$density, method='pearson')^2)
fuv_3025avg_d180<-1-(cor(dd180_30m$density, dd180_25avg$density, method='pearson')^2)

fuv_5025avg_d30<-1-(cor(dd30_50m$density, dd30_25avg$density, method='pearson')^2)
fuv_5025avg_d60<-1-(cor(dd60_50m$density, dd60_25avg$density, method='pearson')^2)
fuv_5025avg_d90<-1-(cor(dd90_50m$density, dd90_25avg$density, method='pearson')^2)
fuv_5025avg_d180<-1-(cor(dd180_50m$density, dd180_25avg$density, method='pearson')^2)

fuv_50avg25avg_d30<-1-(cor(dd30_50avg$density, dd30_25avg$density, method='pearson')^2)
fuv_50avg25avg_d60<-1-(cor(dd60_50avg$density, dd60_25avg$density, method='pearson')^2)
fuv_50avg25avg_d90<-1-(cor(dd90_50avg$density, dd90_25avg$density, method='pearson')^2)
fuv_50avg25avg_d180<-1-(cor(dd180_50avg$density, dd180_25avg$density, method='pearson')^2)


#between 250 and 100
fuv_100250_d30<-1-(cor(dd30_n100$density, dd30_n250$density, method='pearson')^2)
fuv_100250_d60<-1-(cor(dd60_n100$density, dd60_n250$density, method='pearson')^2)
fuv_100250_d90<-1-(cor(dd90_n100$density, dd90_n250$density, method='pearson')^2)
fuv_100250_d180<-1-(cor(dd180_n100$density, dd180_n250$density, method='pearson')^2)
#between 250 repeat and 100
fuv_100250repeat_d30<-1-(cor(dd30_n100$density, dd30_n250_repeat$density, method='pearson')^2)
fuv_100250repeat_d60<-1-(cor(dd60_n100$density, dd60_n250_repeat$density, method='pearson')^2)
fuv_100250repeat_d90<-1-(cor(dd90_n100$density, dd90_n250_repeat$density, method='pearson')^2)
fuv_100250repeat_d180<-1-(cor(dd180_n100$density, dd180_n250_repeat$density, method='pearson')^2)
#between 250 and 250
fuv_250_repeat_d30<-1-(cor(dd30_n250_repeat$density, dd30_n250$density, method='pearson')^2)
fuv_250_repeat_d60<-1-(cor(dd60_n250_repeat$density, dd60_n250$density, method='pearson')^2)
fuv_250_repeat_d90<-1-(cor(dd90_n250_repeat$density, dd90_n250$density, method='pearson')^2)
fuv_250_repeat_d180<-1-(cor(dd180_n250_repeat$density, dd180_n250$density, method='pearson')^2)
#between 500 and 100
fuv_100500_d30<-1-(cor(dd30_n100$density, dd30_n500$density, method='pearson')^2)
fuv_100500_d60<-1-(cor(dd60_n100$density, dd60_n500$density, method='pearson')^2)
fuv_100500_d90<-1-(cor(dd90_n100$density, dd90_n500$density, method='pearson')^2)
fuv_100500_d180<-1-(cor(dd180_n100$density, dd180_n500$density, method='pearson')^2)
#between 100 and 1000
fuv_1001000_d30<-1-(cor(dd30_n100$density, dd30_n1000$density, method='pearson')^2)
fuv_1001000_d60<-1-(cor(dd60_n100$density, dd60_n1000$density, method='pearson')^2)
fuv_1001000_d90<-1-(cor(dd90_n100$density, dd90_n1000$density, method='pearson')^2)
fuv_1001000_d180<-1-(cor(dd180_n100$density, dd180_n1000$density, method='pearson')^2)
#between 500 and 250
fuv_250500_d30<-1-(cor(dd30_n250$density, dd30_n500$density, method='pearson')^2)
fuv_250500_d60<-1-(cor(dd60_n250$density,dd60_n500$density, method='pearson')^2)
fuv_250500_d90<-1-(cor(dd90_n250$density, dd90_n500$density, method='pearson')^2)
fuv_250500_d180<-1-(cor(dd180_n250$density, dd180_n500$density, method='pearson')^2)
#between 500 and 250 repeat
fuv_250500_repeat_d30<-1-(cor(dd30_n250_repeat$density, dd30_n500$density, method='pearson')^2)
fuv_250500_repeat_d60<-1-(cor(dd60_n250_repeat$density,dd60_n500$density, method='pearson')^2)
fuv_250500_repeat_d90<-1-(cor(dd90_n250_repeat$density, dd90_n500$density, method='pearson')^2)
fuv_250500_repeat_d180<-1-(cor(dd180_n250_repeat$density, dd180_n500$density, method='pearson')^2)
#between 1000 and 250
fuv_2501000_d30<-1-(cor(dd30_n250$density, dd30_n1000$density, method='pearson')^2)
fuv_2501000_d60<-1-(cor(dd60_n250$density,dd60_n1000$density, method='pearson')^2)
fuv_2501000_d90<-1-(cor(dd90_n250$density, dd90_n1000$density, method='pearson')^2)
fuv_2501000_d180<-1-(cor(dd180_n250$density, dd180_n1000$density, method='pearson')^2)
#between 1000 and 250 repeat
fuv_2501000_repeat_d30<-1-(cor(dd30_n250_repeat$density, dd30_n1000$density, method='pearson')^2)
fuv_2501000_repeat_d60<-1-(cor(dd60_n250_repeat$density,dd60_n1000$density, method='pearson')^2)
fuv_2501000_repeat_d90<-1-(cor(dd90_n250_repeat$density, dd90_n1000$density, method='pearson')^2)
fuv_2501000_repeat_d180<-1-(cor(dd180_n250_repeat$density, dd180_n1000$density, method='pearson')^2)
#between 500 and 1000
fuv_5001000_d30<-1-(cor(dd30_n500$density, dd30_n1000$density, method='pearson')^2)
fuv_5001000_d60<-1-(cor(dd60_n500$density,dd60_n1000$density, method='pearson')^2)
fuv_5001000_d90<-1-(cor(dd90_n500$density, dd90_n1000$density, method='pearson')^2)
fuv_5001000_d180<-1-(cor(dd180_n500$density, dd180_n1000$density, method='pearson')^2)

####################3
#between 100 and 100 repeated
#fuv_100repeats_d30<-1-(cor(dd30_n100$density, dd30_n100_repeat$density, #method='pearson')^2)
#fuv_100repeats_d60<-1-(cor(dd60_n100$density, dd60_n100_repeat$density, #method='pearson')^2)
#fuv_100repeats_d90<-1-(cor(dd90_n100$density, dd90_n100_repeat$density, #method='pearson')^2)
#fuv_100repeats_d180<-1-(cor(dd180_n100$density, dd180_n100_repeat$density, #method='pearson')^2)
##between 750 and 100
#fuv_100750_d30<-1-(cor(dd30_n100$density, dd30_n750$density, #method='pearson')^2)
#fuv_100750_d60<-1-(cor(dd60_n100$density, dd60_n750$density, #method='pearson')^2)
#fuv_100750_d90<-1-(cor(dd90_n100$density, dd90_n750$density, #method='pearson')^2)
#fuv_100750_d180<-1-(cor(dd180_n100$density, dd180_n750$density, #method='pearson')^2)

#between 100 and 1000
#fuv_1001000_d30<-1-(cor(dd30_n100$density, dd30_n1000$density, #method='pearson')^2)
#fuv_1001000_d60<-1-(cor(dd60_n100$density, dd60_n1000$density, #method='pearson')^2)
#fuv_1001000_d90<-1-(cor(dd90_n100$density, dd90_n1000$density, #method='pearson')^2)
#fuv_1001000_d180<-1-(cor(dd180_n100$density, dd180_n1000$density, #method='pearson')^2)
##between 1000 and 250
#fuv_2501000_d30<-1-(cor(dd30_n250$density, dd30_n1000$density, #method='pearson')^2)
#fuv_2501000_d60<-1-(cor(dd60_n250$density,dd60_n1000$density, #method='pearson')^2)
#fuv_2501000_d90<-1-(cor(dd90_n250$density, dd90_n1000$density, #method='pearson')^2)
#fuv_2501000_d180<-1-(cor(dd180_n250$density, dd180_n1000$density, #method='pearson')^2)
##between 500 and 1000
#fuv_5001000_d30<-1-(cor(dd30_n500$density, dd30_n1000$density, #method='pearson')^2)
#fuv_5001000_d60<-1-(cor(dd60_n500$density,dd60_n1000$density, #method='pearson')^2)
#fuv_5001000_d90<-1-(cor(dd90_n500$density, dd90_n1000$density, #method='pearson')^2)
#fuv_5001000_d180<-1-(cor(dd180_n500$density, dd180_n1000$density, #method='pearson')^2)


###################33

#100 repeat and ...
#between 500 and 100 repeat
#fuv_100repeat500_d30<-1-(cor(dd30_n100_repeat$density, dd30_n500$density, #method='pearson')^2)
#fuv_100repeat500_d60<-1-(cor(dd60_n100_repeat$density, dd60_n500$density, #method='pearson')^2)
#fuv_100repeat500_d90<-1-(cor(dd90_n100_repeat$density, dd90_n500$density, #method='pearson')^2)
#fuv_100repeat500_d180<-1-(cor(dd180_n100_repeat$density, #dd180_n500$density, method='pearson')^2)
#
#fuv_100repeat250_d30<-1-(cor(dd30_n100_repeat$density, dd30_n250$density, #method='pearson')^2)
#fuv_100repeat250_d60<-1-(cor(dd60_n100_repeat$density, dd60_n250$density, #method='pearson')^2)
#fuv_100repeat250_d90<-1-(cor(dd90_n100_repeat$density, dd90_n250$density, #method='pearson')^2)
#fuv_100repeat250_d180<-1-(cor(dd180_n100_repeat$density, #dd180_n250$density, method='pearson')^2)
#
#fuv_100repeat750_d30<-1-(cor(dd30_n100_repeat$density, dd30_n750$density, #method='pearson')^2)
#fuv_100repeat750_d60<-1-(cor(dd60_n100_repeat$density, dd60_n750$density, #method='pearson')^2)
#fuv_100repeat750_d90<-1-(cor(dd90_n100_repeat$density, dd90_n750$density, #method='pearson')^2)
#fuv_100repeat750_d180<-1-(cor(dd180_n100_repeat$density, #dd180_n750$density, method='pearson')^2)
#
#fuv_1001000_d30_repeat<-1-(cor(dd30_n100_repeat$density, #dd30_n1000$density, method='pearson')^2)
#fuv_1001000_d60_repeat<-1-(cor(dd60_n100_repeat$density, #dd60_n1000$density, method='pearson')^2)
#fuv_1001000_d90_repeat<-1-(cor(dd90_n100_repeat$density, #dd90_n1000$density, method='pearson')^2)
#fuv_1001000_d180_repeat<-1-(cor(dd180_n100_repeat$density, #dd180_n1000$density, method='pearson')^2)
#
#
##250 and ...
##between 500 and 250
#fuv_250500_d30<-1-(cor(dd30_n250$density, dd30_n500$density, #method='pearson')^2)
#fuv_250500_d60<-1-(cor(dd60_n250$density, dd60_n500$density, #method='pearson')^2)
#fuv_250500_d90<-1-(cor(dd90_n250$density, dd90_n500$density, #method='pearson')^2)
#fuv_250500_d180<-1-(cor(dd180_n250$density, dd180_n500$density, #method='pearson')^2)
#
##between 750 and 250
#fuv_250750_d30<-1-(cor(dd30_n250$density, dd30_n750$density, #method='pearson')^2)
#fuv_250750_d60<-1-(cor(dd60_n250$density, dd60_n750$density, #method='pearson')^2)
#fuv_250750_d90<-1-(cor(dd90_n250$density, dd90_n750$density, #method='pearson')^2)
#fuv_250750_d180<-1-(cor(dd180_n250$density, dd180_n750$density, #method='pearson')^2)
#
##between 1000 and 250
#fuv_2501000_d30<-1-(cor(dd30_n250$density, dd30_n1000$density, #method='pearson')^2)
#fuv_2501000_d60<-1-(cor(dd60_n250$density,dd60_n1000$density, #method='pearson')^2)
#fuv_2501000_d90<-1-(cor(dd90_n250$density, dd90_n1000$density, #method='pearson')^2)
#fuv_2501000_d180<-1-(cor(dd180_n250$density, dd180_n1000$density, #method='pearson')^2)
#
#
##500 and ...
##between 750 and 250
#fuv_500750_d30<-1-(cor(dd30_n500$density, dd30_n750$density, #method='pearson')^2)
#fuv_500750_d60<-1-(cor(dd60_n500$density, dd60_n750$density, #method='pearson')^2)
#fuv_500750_d90<-1-(cor(dd90_n500$density, dd90_n750$density, #method='pearson')^2)
#fuv_500750_d180<-1-(cor(dd180_n500$density, dd180_n750$density, #method='pearson')^2)
#
#
##between 750 and 1000
#fuv_7501000_d30<-1-(cor(dd30_n750$density, dd30_n1000$density, #method='pearson')^2)
#fuv_7501000_d60<-1-(cor(dd60_n750$density,dd60_n1000$density, #method='pearson')^2)
#fuv_7501000_d90<-1-(cor(dd90_n750$density, dd90_n1000$density, #method='pearson')^2)
#fuv_7501000_d180<-1-(cor(dd180_n750$density, dd180_n1000$density, #method='pearson')^2)
####################################################################################

# Make table
#sumresults<-data.frame(matrix(ncol=0,nrow=15))
#sumresults$x<-c("100","100","100","100","100","100repeat","100repeat","100r#epeat","100repeat","250","250","250","500","500","750")
#sumresults$y<-c("100repeat","250","500","750","1000","250","500","750","100#0","500","750","1000","750","1000","1000")
#sumresults$day90<-c(fuv_100repeats_d30,fuv_100250_d30,fuv_100500_d30,fuv_10#0750_d30,fuv_1001000_d30,fuv_100repeat250_d30,fuv_100repeat500_d30,fuv_100r#epeat750_d30,fuv_1001000_d30_repeat,fuv_250500_d30,fuv_250750_d30,fuv_25010#00_d30,fuv_500750_d30,fuv_5001000_d30,fuv_7501000_d30)
#sumresults$day60<-c(fuv_100repeats_d60,fuv_100250_d60,fuv_100500_d60,fuv_10#0750_d60,fuv_1001000_d60,fuv_100repeat250_d60,fuv_100repeat500_d60,fuv_100r#epeat750_d60,fuv_1001000_d60_repeat,fuv_250500_d60,fuv_250750_d60,fuv_25010#00_d60,fuv_500750_d60,fuv_5001000_d60,fuv_7501000_d60)
#sumresults$day90<-c(fuv_100repeats_d90,fuv_100250_d90,fuv_100500_d90,fuv_10#0750_d90,fuv_1001000_d90,fuv_100repeat250_d90,fuv_100repeat500_d90,fuv_100r#epeat750_d90,fuv_1001000_d90_repeat,fuv_250500_d90,fuv_250750_d90,fuv_25010#00_d90,fuv_500750_d90,fuv_5001000_d90,fuv_7501000_d90)
#sumresults$day180<-c(fuv_100repeats_d180,fuv_100250_d180,fuv_100500_d180,fu#v_100750_d180,fuv_1001000_d180,fuv_100repeat250_d180,fuv_100repeat500_d180,#fuv_100repeat750_d180,fuv_1001000_d180_repeat,fuv_250500_d180,fuv_250750_d1#80,fuv_2501000_d180,fuv_500750_d180,fuv_5001000_d180,fuv_7501000_d180)
#write.csv(sumresults,"fuv_comparisons_results_finerscale.csv")

# Make table
sumresults<-data.frame(matrix(ncol=0,nrow=6))
sumresults$x<-c("100","100","100","250","250","500")
sumresults$y<-c("250","500","1000","500","1000","1000")
sumresults$day30<-c(fuv_100250_d30,fuv_100500_d30,fuv_1001000_d30,fuv_250500_d30,fuv_2501000_d30,fuv_5001000_d30)
sumresults$day60<-c(fuv_100250_d60,fuv_100500_d60,fuv_1001000_d60,fuv_250500_d60,fuv_2501000_d60,fuv_5001000_d60)
sumresults$day90<-c(fuv_100250_d90,fuv_100500_d90,fuv_1001000_d90,fuv_250500_d90,fuv_2501000_d90,fuv_5001000_d90)
sumresults$day180<-c(fuv_100250_d180,fuv_100500_d180,fuv_1001000_d180,fuv_250500_d180,fuv_2501000_d180,fuv_5001000_d180)
write.csv(sumresults,"/home/tely/LAPS/fuv_comparisons_results_finerscale_with1000.csv")
####
sumresults_avgdepth<-data.frame(matrix(ncol=0,nrow=13))
sumresults_avgdepth$x<-c("0m","5m","10m","20m","30m","50m","0m","5m","10m","20m","30m","50m","25m avg")
sumresults_avgdepth$y<-c("25 m avg","25 m avg","25 m avg","25 m avg","25 m avg","25 m avg","50 avg","50 avg","50 avg","50 avg","50 avg","50 avg","50 avg")
sumresults_avgdepth$day30<-c(fuv_025avg_d30,fuv_525avg_d30,fuv_1025avg_d30,fuv_2025avg_d30,fuv_3025avg_d30,fuv_5025avg_d30,fuv_050avg_d30,fuv_550avg_d30,fuv_1050avg_d30,fuv_2050avg_d30,fuv_3050avg_d30,fuv_5050avg_d30,fuv_50avg25avg_d30)
sumresults_avgdepth$day60<-c(fuv_025avg_d60,fuv_525avg_d60,fuv_1025avg_d60,fuv_2025avg_d60,fuv_3025avg_d60,fuv_5025avg_d60,fuv_050avg_d60,fuv_550avg_d60,fuv_1050avg_d60,fuv_2050avg_d60,fuv_3050avg_d60,fuv_5050avg_d60,fuv_50avg25avg_d60)
sumresults_avgdepth$day90<-c(fuv_025avg_d90,fuv_525avg_d90,fuv_1025avg_d90,fuv_2025avg_d90,fuv_3025avg_d90,fuv_5025avg_d90,fuv_050avg_d90,fuv_550avg_d90,fuv_1050avg_d90,fuv_2050avg_d90,fuv_3050avg_d90,fuv_5050avg_d90,fuv_50avg25avg_d90)
sumresults_avgdepth$day180<-c(fuv_025avg_d180,fuv_525avg_d180,fuv_1025avg_d180,fuv_2025avg_d180,fuv_3025avg_d180,fuv_5025avg_d180,fuv_050avg_d180,fuv_550avg_d180,fuv_1050avg_d180,fuv_2050avg_d180,fuv_3050avg_d180,fuv_5050avg_d180,fuv_50avg25avg_d180)
write.csv(sumresults_avgdepth,"/Users/taylorely/Documents/OceanModeling/fuv_comparisons_results_avgdepths.csv")


```



